---
title: "Assigment - kNN DIY"
author:
  - name author here - Mendy
  - name reviewer here - Eilis
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---


```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
```

---




## Business Understanding
We will be using 4 variables to observe whether an office has been used or not. However, the table provides too much information - so, irrelevant information will be excluded.

## Data Understanding
```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/data-mining-s2y2122-Mendy1997/master/datasets/KNN-occupancy.csv"
```

```{r}
rawDF <- read_csv(url)
str(rawDF)
```


# Data preparation
The variable 'date' does not contain any important information, thus will be excluded. 

```{r}
cleanDF <- rawDF[-1]
head(cleanDF)
```

We will use this formula to see how many offices are occupied or not, (1: occupancy, 0: not occupied)

```{r}
cntDiag <- table(cleanDF$Occupancy)
propDiag <- round(prop.table(cntDiag) * 100 , digits = 1)
cntDiag
```

```{r}
propDiag
```

We will now change the "1" and "0" into "occupancy" and "not occupied"

```{r}
cleanDF$Occupancy <- factor(cleanDF$Occupancy, levels = c("1", "0"), labels = c("Yes", "No")) %>% relevel("No")
head(cleanDF, 10)
```


```{r}
summary(cleanDF)
```

```{r}
normalize <- function(x) { # Function takes in a vector
  return ((x - min(x)) / (max(x) - min(x))) # distance of item value - minimum vector value divided by the range of all vector values
}
testSet1 <- c(1:5)
testSet2 <- c(1:5) * 10
cat("testSet1:", testSet1, "\n")
```

```{r}
cat("testSet2:", testSet2, "\n")
```

```{r}
cat("Normalized testSet1:", normalize(testSet1), "\n")
```

```{r}
cat("Normalized testSet2:", normalize(testSet2))
```

```{r}
nCols <- dim(cleanDF)[2]
cleanDF_n <- sapply(1:(nCols-1),
                    function(x) {
  normalize(cleanDF[,x])
}) %>% as.data.frame()

summary(cleanDF_n)
```

# Training the data

```{r}
trainDF_feat <- cleanDF_n[1:5000,  ]
testDF_feat <- cleanDF_n[5001:8143,  ]
```


```{r}
trainDF_labels <- cleanDF[1:5000,  6]
testDF_labels <- cleanDF[5001:8143,  6]
```

# Modeling

```{r}
cleanDF_test_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), cl = as.matrix(trainDF_labels), k = 31)

head(cleanDF_test_pred)
```

# Evaluation and Deployment


```{r}
confusionMatrix(cleanDF_test_pred, testDF_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))
```



##Notes of reviewer
#line 63 I changed cleanDF$diagnosis to cleanDF$Occupancy to change the right column in the table
#line 69 I changed summary(cleanDF[c("Temperature", "Humidity", "Light", "CO2")]) to summary(cleanDF) to show a better summary
#Line 94 I changed the sapply(2) to sapply(1)
#Line 100 I removed the c("Temperature", "Humidity", "Light", "CO2", "HumidityRatio")
#Line 106 I changed the numbers from 4000 to 5000 and removed the 7 and the end
#Line 107 I changed the the number 4001 to 5001 and removed the 7
# I added lines 112 and 113 since they were missing
# Line 119 I changed the k = 57 to k = 31
# Line 128 I changed the positive = occupancy to positive = NULL to make the code work
